Predicting _C. difficile_ Infection Severity from the Taxonomic Composition of the Gut Microbiome

### 2023-06-01 paper/paper.qmd
Remove pragmatic intersection from performance plot
It's cleaner this way. It's the same as attributable anyway

::: {#fig-performance fig-cap="**Performance of ML models.**
In the left facets, models were trained on the full datasets, with different
numbers of samples available for each severity definition.
In the right facets, models were trained on the same dataset consisting of the
intersection of samples with all labels available for each definition.
Note that the intersection dataset for Attributable and Pragmatic severity have
exactly the same labels, thus they have identical performance.
**A)** 
Area under the receiver-operator characteristic curve (AUROC) for the test sets
and cross-validation folds of the training sets, and the area under the balanced
precision-recall curve (AUBPRC) for the test sets.
Each point is the median performance across 100 train/test splits with tails as
the 95% CI.
Nearly all pairs of definitions have significantly different performances on the
test set (P < 0.05) except for AUROC and AUBPRC of Attributable vs. Pragmatic on
the intersection dataset (as they are identical), AUROC of Attributable vs.
All-cause on the full dataset, and AUROC of Attributable vs. IDSA on the full
dataset.
**B)** Receiver-operator characteristic curves for the test sets.
Mean specificity is reported at each sensitivity value, 
with ribbons as the 95% CI.
**C)** Balanced precision-recall curves for the test sets.
Mean balanced precision is reported at each recall value, 
with ribbons as the 95% CI.
"}
![](figures/ml-performance.png)
:::

>>>>

::: {#fig-performance fig-cap="**Performance of ML models.**
In the left facets, models were trained on the full datasets, with different
numbers of samples available for each severity definition.
In the right facets, models were trained on the same dataset consisting of the
intersection of samples with labels available for all definitions.
Note that the intersection dataset has exactly the same labels for attributable
and pragmatic severity, thus these have identical performance.
**A)** 
Area under the receiver-operator characteristic curve (AUROC) for the test sets
and cross-validation folds of the training sets, and the area under the balanced
precision-recall curve (AUBPRC) for the test sets.
Each point is the median performance across 100 train/test splits with tails as
the 95% CI.
**B)** Receiver-operator characteristic curves for the test sets.
Mean specificity is reported at each sensitivity value, 
with ribbons as the 95% CI.
**C)** Balanced precision-recall curves for the test sets.
Mean balanced precision is reported at each recall value, 
with ribbons as the 95% CI.
"}
![](figures/ml-performance.png)
:::
